Online Multiclass Linear Classification with Bandit Feedback

### 2019-01-09 ICML-submission/introduction.tex
Fix formatting of definitions

In this paper, we focus on the special case when the examples chosen by the
adversary lie in $\R^d$ and
are \emph{linearly separable with a margin}
(see Definition~\ref{def:linear-sep} for a formal description).
%\chicheng{I wonder if we should introduce the two notions of linear separability here,
%because strong linear separability is also worth mentioning in the full-information setting.
%}
%\david{The formal definitions are in a section of their own.}

@@

The bandit feedback setting, however, is much more challenging. To understand
the differences, we dissect the notion of linear separability in the multiclass
setting. Besides the standard notion of linear separability, we also consider
\emph{strong linear separability} (see Definition~\ref{def:strong-linear-sep} for a formal description). For binary classification, these two
definitions are identical.
However, they differ for multiclass classification with $K \geq 3$.
For multiclass classification with $K$ classes, the standard notion of linear
separability means that the examples from each class lie in an intersection of
$K-1$ halfspaces and the examples outside of the class lie in the complement of
the intersection of the halfspaces. Strong linear separability means that
examples from each class are separated from the remaining examples by a
\emph{single} hyperplane. We state the definitions precisely in
Section~\ref{section:notions-of-linear-separability}.

>>>>

In this paper, we focus on the special case when the examples chosen by the
adversary lie in $\R^d$ and are \emph{linearly separable with a margin} (see
\autoref{definition:linear-separability} for a formal description).
%\chicheng{I wonder if we should introduce the two notions of linear separability here,
%because strong linear separability is also worth mentioning in the full-information setting.
%}
%\david{The formal definitions are in a section of their own.}

@@

The bandit feedback setting, however, is much more challenging. To understand
the differences, we dissect the notion of linear separability in the multiclass
setting. Besides the standard notion of linear separability, we also consider
\emph{strong linear separability} (see
\autoref{definition:strong-linear-separability} for a formal description). For
binary classification, these two definitions are identical. However, they differ
for multiclass classification with $K \geq 3$. For multiclass classification
with $K$ classes, the standard notion of linear separability means that the
examples from each class lie in an intersection of $K-1$ halfspaces and the
examples outside of the class lie in the complement of the intersection of the
halfspaces. Strong linear separability means that examples from each class are
separated from the remaining examples by a \emph{single} hyperplane. We state
the definitions precisely in
Section~\ref{section:notions-of-linear-separability}.

### 2019-01-09 ICML-submission/notions-of-linear-separability.tex
Fix formatting of definitions

\begin{definition}[Linear separability]
Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, and $\gamma$ be a positive real number. Let $(x_1, y_1), (x_2,
y_2), \dots, (x_T, y_T)$ be labeled examples in $V \times \{1,2,\dots,K\}$.

The examples are said to be \emph{linearly separable with a
margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
that
\begin{align}
\label{equation:linear-separability-1}
\sum_{i=1}^K \norm{w_i}^2 & \le 1 \; , \\
\label{equation:linear-separability-2}
\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_{y_t}} & \ge \ip{x_t}{w_i} + \gamma \; .
\end{align}
\label{def:linear-sep}
\end{definition}

\begin{definition}[Strong linear separability]
Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, and $\gamma$ be a positive real number. Let $(x_1, y_1), (x_2,
y_2), \dots, (x_T, y_T)$ be labeled examples in $V \times \{1,2,\dots,K\}$.

The examples are said to be \emph{strongly linearly separable with a
margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
that
\begin{align}
\label{equation:strong-linear-separability-1}
\sum_{i=1}^K \norm{w_i}^2 & \le 1 \; , \\
\label{equation:strong-linear-separability-2}
\forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} &\ge \gamma \; , \\
\label{equation:strong-linear-separability-3}
\forall t \in \{1,2,\dots,T\} \qquad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_i} & \le - \gamma \; .
\end{align}
\label{def:strong-linear-sep}
\end{definition}

>>>>

\begin{definition}[Linear separability]
\label{definition:linear-separability}
Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, and $\gamma$ be a positive real number. Let $(x_1, y_1), (x_2,
y_2), \dots, (x_T, y_T)$ be labeled examples in $V \times \{1,2,\dots,K\}$.

The examples are said to be \emph{linearly separable with a
margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
that
\begin{align}
\label{equation:linear-separability-1}
& \sum_{i=1}^K \norm{w_i}^2 \le 1 \; , \\
\label{equation:linear-separability-2}
& \begin{gathered}
\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
\ip{x_t}{w_{y_t}} \ge \ip{x_t}{w_i} + \gamma \; .
\end{gathered}
\end{align}
\end{definition}

\begin{definition}[Strong linear separability]
\label{definition:strong-linear-separability}
Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, and $\gamma$ be a positive real number. Let $(x_1, y_1), (x_2,
y_2), \dots, (x_T, y_T)$ be labeled examples in $V \times \{1,2,\dots,K\}$.

The examples are said to be \emph{strongly linearly separable with a
margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
that
\begin{align}
\label{equation:strong-linear-separability-1}
& \sum_{i=1}^K \norm{w_i}^2 \le 1 \; , \\
\label{equation:strong-linear-separability-2}
& \forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} \ge \gamma \; , \\
\label{equation:strong-linear-separability-3}
& \begin{gathered}
\forall t \in \{1,2,\dots,T\} \qquad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
\ip{x_t}{w_i} \le - \gamma \; .
\end{gathered}
\end{align}
\end{definition}
